Abstractions for Multi-Sorted Substitutions

### 2024-03-18 paper/paper.tex
Update.

%\nolinenumbers %uncomment to disable line numbering

@@

  In this paper, we present a simplified version of the actual
  framework, focusing on the core concepts. We present all necessary
  definitions and lemmas, but omit some proofs for the sake of
  space. The omitted proofs can be found in our supplementary material,
  which includes the simplified framework (368 lines of code) and the
  System F formalization (221 lines of code).
  The full framework including the case studies is available on Github:
  \textcolor{blue}{\url{https://github.com/m0rphism/kitty}}
  % The full framework is available online.\footnote{See supplementary material. In the final version, this text will be replaced by a link to github.}

>>>>

% \nolinenumbers %uncomment to disable line numbering

@@

  In this paper, we present a simplified version of the actual
  framework, focusing on the core concepts. We present all necessary
  definitions and lemmas, but omit some proofs for the sake of
  space. The omitted proofs can be found in our supplementary material,
  which includes the simplified framework (368 lines of code) and the
  System F formalization (212 lines of code, of which 79 can be derived in the full framework).
  The full framework including the case studies is available on Github:
  \textcolor{blue}{\url{https://github.com/m0rphism/kitty}}
  % The full framework is available online.\footnote{See supplementary material. In the final version, this text will be replaced by a link to github.}
